\documentclass[a4paper]{article}
\usepackage[cm]{fullpage}
\usepackage{array}
\usepackage{longtable}

\author{Sean Enderby}
\title{Thesis Revisions \\
	\Large Timbral Control of Audio Through Harmonic Excitation}
\date{}

\renewcommand{\familydefault}{\sfdefault}

\newcolumntype{C}[1]{>{\centering}p{#1}}
\newcommand{\answer}[1]{\underline{\underline{#1}}}

\begin{document}
\maketitle

\begin{center}
	\begin{longtable}{|c|C{8cm}|C{8cm}|}
		\hline 
		\bf{No.} & \bf{Revision} & \bf{Action Taken} \tabularnewline
		\hline
		1. & Review the abstract to ensure that the contribution to knowledge is more explicit & \tabularnewline
		\hline
		2. & Review the acronym list for completeness & Entries for ADSR, AMDF, API, AU, EQ, ERB, HPS, LFO, MUSHRA,
			RDF, SAFE and VST added to the acronym list \tabularnewline
		\hline
		3. & The mathematical notation list lacks Mahalanobis distance & \tabularnewline
		\hline
		4. & In Chapter 1 add flowchart of key stages of audio development process & \tabularnewline
		\hline
		5. & Add PCA equation on p26 & \tabularnewline
		\hline
		6. & Fig 5.12 should be moved to the appropriate place in Chapter 3 & Figure moved to Section~3.5.8 and
			accompanying text in that section altered. Relevant text in the spectral folding subsection of
			Section~5.2.4 also altered. \tabularnewline
		\hline
		7. & Amend axis labelling on Figs 3.4. 3.5 and the former Fig 5.12 to add correct frequency figures &
			Figures~3.4 to 3.6 now have frequency axis labels at 0 and $\frac{f_{s}}{2}$ \tabularnewline
		\hline
		8. & In s4.2.2, adjust motivation for plugins & Extended the penultimate paragraph of
			Section~4.2.2 to mention the additional APIs provided by some DAWs.\tabularnewline
		\hline
		9. & In s4.2.3, add justification for 5-second plugin sample size & Altered the second
			paragraph of Section~4.2.3 to mention engineers configuring effect using short loops of audio
			as discussed in the Viva.\tabularnewline
		\hline
		10. & On pp68-70, explain how much variance is explained by principal components & First
			paragraph of each of the subsections in Section~4.3.5 altered to include the proportion of
			total variance described by the timbre space. \tabularnewline
		\hline
		11. & On the plots with principal components in Chapter 4, ensure that numbering on axes is complete &
			\tabularnewline
		\hline
		12. & In chapter 4, explain what happens to PC4 and PC5 & Note about the lack of patterns in PCs 4 and 5
			included in the same paragraphs as changed for revision 10. \tabularnewline
		\hline
		13. & On p96 equation 5.13, the derivation for integrator for series should be included (eg in an Appendix
			as discussed below) & Derivation of Fourier series coefficients given in Appendix~A.2.  Derivation
			of the Fourier series for full wave rectification (Equation~5.11) also included as Appendix~A.1 for
			completeness.  References added to the text in the relevant sections, linking to the appendices.
			\tabularnewline
		\hline
		14. & Figs 5.8-5.11 and 5.14 need replotting for greater clarity & Unprocessed signal moved to its
			own figure (Figure~5.8), the processed signals for the multiplier, SSBA and IAP techniques then
			shown on their own in Figures~5.9 to 5.12. Spectra of signal processed by STTR split into
			subfigures in Figure~5.14 \tabularnewline
		\hline
		15. & On p99, the description of IAP should mention and reference its relationship to complex FM synthesis &
			First paragraph of the IAP subsection of Section~5.2.4 altered to reference Le Brun describing the
			spectrum of complex FM.  \tabularnewline
		\hline
		16. & s5.2.5 should mention the square wave appearance of the signal & Second paragraph of Section~5.2.5
			altered to mention square waves. \tabularnewline
		\hline
		17. & On p100, correct the cutoff frequency reference at top of page & Expression corrected to
			$\left( \frac{f_{2}}{2} - f \right)$Hz. \tabularnewline
		\hline
		18. & In Chapter 6, ensure complete descriptions of the filters used are given (eg in an Appendix as
			discussed below) & \tabularnewline
		\hline
		19. & On p118, place a methodology discussion within the dedicated evaluation methodology section and
			describe and justify test signals used in the final paragraph & Methodology section added
			(Section~6.3.1), more detail added about the parameterisation process (mentioning derivation of parameter /
			feature relationship formulae). \tabularnewline
		\hline
		20. & On p125, give full derivation of equation 6.6 (eg in an Appendix as discussed below) &
			Derivation of spectral flatness parameterisation given in Appendix~A.3. Reference to that appendix
			added to the text. \tabularnewline
		\hline
		21. & Be consistent in use of tristimulus/tristimuli & Usage is consistent: the singular "tristimulus" is
			used when referring to the metric and single values, the plural "tristimuli" used when talking about
			multiple values from multiple signals "the first tristimuli of the test signals". \tabularnewline
		\hline
		22. & Table 6.1 (p135) should be moved to s6.3 & Table moved to its own section (Section~6.3.1).
			Second paragraph in the conclusion section of Chapter~6 adjusted accordingly. \tabularnewline
		\hline
		23. & The first 2 sentences of Chapter 7 can be deleted & Deleted those two sentences. \tabularnewline
		\hline
		24. & Expand the second paragraph of Chapter 7 to explain the experimental methodology used & Paragraph
			extended to include short descriptions of the objective and subjective testing undertaken
			\tabularnewline
		\hline
		25. & In s7.2.2, insert a flow diagram to clearly explain operation of synthesis systems & Figure~7.1 updated
			to be more descriptive and preceding paragraph extended better explaining the operation. Figure~7.2
			also updated to include $f_{0}$ tracker. \tabularnewline
		\hline
		26. & Explain the colour coding, and increase the size of, Figs 7.4 and 7.6 & Figure size increased
			and the text of the first paragraph in the Subjective Evaluation subsection of Section~7.2.2 amended
			to explain the use of colour. \tabularnewline
		\hline
		27. & In s7.3.4, clarify and explain the derivation of percentages and their relationship with heat maps &
			Fifth paragraph of Section~7.3.4 extended explaining which cells of the heat map are summed.
			\tabularnewline
		\hline
		28. & In s8.4.2, improve the clarity of the second paragraph to deal separately with monotonic and
			polyphonic signals, perhaps as 2 paragraphs & \tabularnewline
		\hline
		29. & The section on further work needs to identify future work directly emerging from the thesis &
			\tabularnewline
		\hline
		30. & Throughout, review the use of `conclusion', `conclusions' and `summary', particularly at the end of
			each chapter & Usage reviewed and decisions made as follows. Literature review
			chapters (2, and 3) are ended with a Summary section summarising the findings given in the
			literature. Research content (Chapters 4, 5, 6 and Sections 7.2 and 7.3) are concluded with a
			Conclusion section. Chapter 7 then ends with a Summary section to summarise the finding of the two
			experiments in that chapter. To keep this patter the title of Chapter~6 has been
			changed from ``Conclusions'' to ``Conclusion''. \tabularnewline
		\hline
		31. & Provide a new Appendix to list software contributions and tools used & \tabularnewline
		\hline
		32. & Carry out a final proof read of the revised text & \tabularnewline
		\hline
	\end{longtable}
\end{center}
\end{document}
